### 2019-04-01 thesis-template/msc-thesis.tex
update

\chapter*{Abstract}
%\input{abstract}
Tensor Fields, are most commonly associated with stress distributions (cnf. Cauchy-Stress Tensor) in 2D/3D grids, but also have some other meanings in practice in physics. By means of global illumination techniques we develop a new method to visualize tensor fields. As a basis, we derive a simple light propagation scheme for Cartesian grids, which satisfies propagation attenuation and energy-conservation principles and is able to approximate light distributions for given light source position(s) and direction(s) until convergence. The transmission profiles within this grid are considered as crystal fiber structures as an underlying physical model (eg. gemstones: tiger's eye's cat's eye effect). The consequent task is to model anisotropic fibre structures with the orientation and anisotropy measures of the underlying tensor field in the grid.
For this, we create an eigenframe by PCA (principal component analysis) for every cell of the tensor field and form an ellipsoid equation as transmission (transfer/weighting) function for the transmitted light profiles. We measure impulse responses of the tensor field with Delta-Pulses as light sources at any (sampled) position and in any direction to generate a uniform sampled map of the global illumination distributions. This map is considered as a global illumination energy flow field.
We gain inspiration by vector field particle tracing's FTLE approach for analyzing the gradient of the flow field of the resulting light distributions. Similar to how the FTLE detects ridges/LCS (Lagrangian Coherent Structures) in vector fields (flow fields), our approach captures these structures likewise, attracting/repelling/saddling tensor field lines (TFL) which frequently represent key structures in nature, in tensor fields. Note that the resulting scalar field is $(n+1)$-dimensional ($x,y,z$ and direction $\theta$) and needs to be flattened by averaging or projection in 3D for proper visualization. We denote this entity a global illumination gradient which states an FTLE-related approach for visualizing LCS in tensor fields through analysis of the global and light transport  directed by imprint/engraving in crystelline fiber structures. 
We also introduce Deformation Ellipsoid Glyphs which are, additionally to visualizing anisotropic topology, pointing inward/outward for compressive/tensile stresses visualizing orientation of mechanical stresses.
We evaluate our approaches for plausibility and comparability within an extensive test campaign.
\newpage

@@

Tensor Field Visualization is gaining importance as a relevant tool for the analysis of fluid and solid mechanics. Tensors are found most commonly in medical, scientific and engineering applications. A tensor is a $n$-D generalization of a matrix and appears e.g. as Jacobi-Matrix in Flow Fields or as stress tensor in solid continuum mechanics. Basically, tensors describe stretchings, rotations and volume changes in both solid and fluid material. While most techniques focus on symmetric tensor field visualization (like Glyphs and Tensor Field Lines), some other recent works adress the problem of asymmetric tensor field visualization. The issue with asymmetric or antisymmetric tensors is that they do not always yield real eigenvalues, which is needed to determine an eigenbasis to set up glyphs, hyperstreamlines or tensor field lines. \cite{zheng} et.al. proposed the concept of dual eigenvectors and \cite{zhang} eigenvector manifold and eigenvalue manifold to visualize eigenvectors in the complex domain. The concept of Tensor Magnitude has been introduced by \cite{laramee} for means of physical interpretation and proposed an efficient glyph and hyperstreamline hybrid approach, which made dynamic interaction in real-time in 2D tensor fields feasible.\\

@@

\section{(Beispiel) Netzwerke}
\label{sec:networks}

\section{(Beispiel) Informationsextraktion}
\label{sec:ie}

\section{Verwandte Arbeiten}
\label{sec:related}

Typischerweise im letzten Abschnitt dieses Kapitels wird dann auf
verwandte Arbeiten eingegangen. Entsprechende Arbeiten sind geeignet
zu zitieren. Beispiel: Die wurde erstmalig in den Arbeiten von Spitz
und Gertz \cite{Spitz2016a} gezeigt \ldots Details dazu werden in
dem Buch von Newman zu Netzwerken \cite{Newman2010} erläutert \ldots.

>>>>

\chapter*{Abstract}
%\input{abstract}
Tensor Fields, are most commonly associated with stress distributions (cnf. Cauchy-Stress Tensor) in 2D/3D grids, but also have some other meanings in practice in physics. By means of global illumination techniques we develop a new method to visualize tensor fields. As a basis, we derive a simple light propagation scheme for Cartesian grids, which satisfies propagation attenuation and energy-conservation principles and is able to approximate light distributions for given light source position(s) and direction(s) until convergence. The transmission profiles within this grid are considered as crystal fiber structures as an underlying physical model (eg. gemstones: tiger's eye's cat's eye effect). The consequent task is to model anisotropic fibre structures with the orientation and anisotropy measures of the underlying tensor field in the grid.
For this, we derive an eigenbasis by PCA (principal component analysis) for every cell of the tensor field and form an ellipsoid equation as transmission (transfer/weighting) function for the transmitted light profiles. We measure impulse responses of the tensor field with Delta-Pulses as light sources at any (sampled) position and in any direction to generate a uniform sampled map of the global illumination distributions. This map is considered as a global illumination energy flow field.
We gain inspiration by vector field particle tracing's FTLE approach for analyzing the gradient of the flow field of the resulting light distributions. Similar to how the FTLE detects ridges/LCS (Lagrangian Coherent Structures) in vector fields (flow fields), our approach captures these structures likewise, attracting/repelling/saddling tensor field lines (TFL) which frequently represent key structures in nature, in tensor fields. Note that the resulting scalar field is $(n+1)$-dimensional ($x,y,z$ and direction $\theta$) and needs to be flattened by averaging or projection in 3D for proper visualization. We denote this entity a global illumination gradient which states an FTLE-related approach for visualizing LCS in tensor fields through analysis of the global and light transport  directed by imprint/engraving in crystelline fiber structures. 
We also introduce Deformation Ellipsoid Glyphs which are, additionally to visualizing anisotropic topology, pointing inward/outward for compressive/tensile stresses visualizing orientation of mechanical stresses.
We evaluate our approaches for plausibility and comparability within an extensive test campaign.
\newpage

@@

Tensor Field Visualization is gaining importance as a relevant tool for the analysis of fluid and solid mechanics. Tensors are found most commonly in medical, scientific and engineering applications. A tensor is a $n$-D generalization of a matrix and appears e.g. as Jacobi-Matrix in Flow Fields or as stress tensor in solid continuum mechanics. Basically, tensors describe stretchings, rotations and volume changes in both solid and fluid material. While most techniques focus on symmetric tensor field visualization (like Glyphs and Tensor Field Lines), some other recent works adress the problem of asymmetric tensor field visualization. The issue with asymmetric or antisymmetric tensors is that they do not always yield real eigenvalues, which is needed to determine an eigenbasis to set up glyphs, hyperstreamlines or tensor field lines. \cite{pang&zheng} et.al. proposed the concept of dual eigenvectors and \cite{zhang} eigenvector manifold and eigenvalue manifold to visualize eigenvectors in the complex domain. The concept of Tensor Magnitude has been introduced by \cite{laramee} for means of physical interpretation and proposed an efficient glyph and hyperstreamline hybrid approach, which made dynamic interaction in real-time in 2D tensor fields feasible.\\

@@

\section{(Beispiel) Tensoren}
\label{sec:networks}

\section{(Beispiel) HAT}
\label{sec:ie}

\section{Related Work}
\label{sec:related}

There has been extensive recent work on symmetric tensors but not on asymmetric ones.  Since we aren't able to cover the whole scope in this work, we will focus on the most relevant works about tensor field visualization.

\textbf{Symmetric Tensor Field Visualization}\\
\cite{pang&zheng} et.al. proposed a texture-based visualization approach called HyperLIC, which extends the concept of LIC to symmetric tensor fields by using an anisotropic 2D-filter kernel oriented along the major/minor eigenvectors. The notion of tensor field topology and the concept of Hyperstreamlines was first introduced by \cite{delmarcelle&hesselink}. The placement of tensor field lines as hyperstreamlines was recently improved by \cite{spencer} et.al. for glyph packing. \cite{feng} et. al. used Voronoi Tesselation for placing the glyphs. Superquadric glyphs have been proposed by \cite{Schultz&Kindlmann} for better flexibility for non-positive definite tensors. \cite{deleeuw&vanwijk} visualize the partial derivative gradient, the Jacobian of the tensor field.
\\
\textbf{Asymmetric Tensor Field Visualization}\\
\cite{pang&zheng}
Typischerweise im letzten Abschnitt dieses Kapitels wird dann auf
verwandte Arbeiten eingegangen. Entsprechende Arbeiten sind geeignet
zu zitieren. Beispiel: Die wurde erstmalig in den Arbeiten von Spitz
und Gertz \cite{Spitz2016a} gezeigt \ldots Details dazu werden in
dem Buch von Newman zu Netzwerken \cite{Newman2010} erläutert \ldots.
